The Astropy Project

### 2018-01-04 main.tex
update of the title
fixed cosmology subpackage

The \package{cosmology} package contains classes for representing different
cosmologies and functions for calculating commonly used quantities such as
look-back time and distance.   The package was described in detail in
\cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
the values in \cite{2016A&A...594A..13P}.

@@

We would like to thank the members of the community that have 
contributed to \astropy, 
that have opened issues and provided feedback, and have supported the 
project in a number of different ways.  We would like to acknowledge
Alex Conley and Neil Crighton for maintaining the  \package{cosmology} 
package. 
%insert significant contributors to astropy who have decided not to 
%be co-authors

>>>>

The \package{cosmology} subpackage contains classes for representing different
cosmologies and functions for calculating commonly used quantities such as
look-back time and distance.   The subpackage was described in detail in
\cite{astropy}.  The default cosmology in \astropypkg version 2.0 is given by
the values in \cite{2016A&A...594A..13P}.

@@

We would like to thank the members of the community that have 
contributed to \astropy, 
that have opened issues and provided feedback, and have supported the 
project in a number of different ways.  We would like to acknowledge
Alex Conley and Neil Crighton for maintaining the  \package{cosmology} 
subpackage. 
%insert significant contributors to astropy who have decided not to 
%be co-authors
